\sffamily An EEG-based visual Brain-Computer Interface for gaze-free communication

### 2024-09-22 chapters/wcble.tex
Add decoders

\section{Introduction}

@@

\subsection{Existing methods for latency estimation and alignment}

\subsubsection{Single-component approaches}
The most straight-forward method to estimate single-trial latency
peak-picking. Here, the latency of an ERP is determined as the
time-point of it's maximum (or minimum) amplitude with relaion to the stimulus
onset. While straight-forward, this method
does not perform well in low or negative SNR conditions, unless combined with
filtering. Filtering can suppress the noise contaminating EEG trials, lowering
the risk of picking a noise peak instead of a true peak of the ERP. Several filtering approaches have been developed to be used in
conjuction with peak-picking, in the time domain~\cite{Carlton1980, McCarthy1981,
	Karjalainen1999, Nishida1999,  Sparacino2002, Georgiadis2005,
	D’Avanzo2011} and in the time-frequency
domain~\cite{Quiroga2003, wang2007single,Hu2010,arico2014influence}. Filtering can
also be done in the spatial domain. The spatial filter can be constructed
using PCA~\cite{Ouyang2017}, ICA~\cite{townsend1999analyzing, jung2001analysis,
	Milne2011}, or as a spatial LCMV beamformer~\cite{TREDER2016279}.

@@

\subsubsection{Multi-component approaches}
The abovementioned methods do not take into account the fact that  ERPs are multi-component signals. Multiple components can be time-locked to different events or neurophysiological proccess and hence are not necessarily
time-locked to each other. They each can have different latency
variabilities. The presence of more than one component can hamper the
performance of some algorithms, and it often only possible to extract only the
latencies of the largest component present~\cite{Ouyang2017}. When aligning trials
to one component and averaging, this will introduce blurring in the other
components~\cite{Ouyang2020}.

@@

\subsubsection{Contribution}
In this work, we introduce a new latency method that leverages data-driven,
joint spatiotemporal filtering based on the LCMV beamformer~\cite{Vliet2016}. The algorithm
integrates the spatiotemporal filtering in Woody's template matching iteration
scheme and can easily be extended to multi-component settings.
Our method attempts to model the spatial and temporal activation of
each ERP component, as well as it's latency distribution, and takes into acount the
spatial and temporal correlation of the EEG background noise.

\section{Introduction}
Single-trial ERP latency jitter introduces a problem in ERP analysis:
the \textit{smearing effect} occurs when aggregating over multiple identical
signals with different latencies.
A familiar example of this happens when averaging over jittered epochs for ERP
analysis.
In the presence of jitter, the shape and amplitude of the average do not
reflect the properties of the original signal.
As the smearing effect reduces the amplitude of the average,
it negatively impacts the signal-to-noise ratio (SNR).
The smearing effect equally impacts the SNR of information captured by a
classifier's parameters when training with a procedure that does not account for
this jitter, and thus also affects its performance~\cite{Thompson2012}.
Hence, effective latency estimation and jitter compensation can contribute to higher
decoding performance.
%In this work, we propose a latency estimation and alignment strategy based on
%the method proposed by \cite{Thompson2012}.

@@

@@

\section{Materials and Methods}
\subsection{Decoders}
\subsubsection{Classifier-based Latency Estimation}
\label{sec:cble}

@@

\subsubsection{Robust CBLE latency features}
\label{sec:robust-latency}
The ERP decoding method based on CBLE introduced by \cite{Mowla2017} does
not make use of the extracted latencies, only passing score matrix $\mat{Y}$ on
to the second-stage classifier.
%Furthermore, previous CBLE works~\cite{Thompson2012,Mowla2020} only used these
%latencies to correlate them with neurophysiological processes or to predict
%decoder performance.
We noticed that, while CBLE performance was unaffected, the classification
performance of our proposed method can be improved if the estimated
latencies are also made available as features to the second-stage classifier,
after a square transform for linear separability~\cite{Thompson2012}.

@@

\subsubsection{Classifier-based Latency Estimation with Woody
	Iterations}
To improve performance over CBLE, we propose a new algorithm inspired both by
CBLE and the aforementioned Woody iteration scheme (WCBLE).
Instead of using CBLE to estimate the features of a second-stage classifier
directly, CBLE latency estimation is used as a step in a Woody iteration scheme.
While the Woody algorithm iteratively enhances the SNR of an ERP template to
cross-correlate with the data, WCBLE iteratively re-estimates the parameters of
the first-stage classifier.
To improve convergence and perform well in a classification setting, WCBLE
aligns both targets and non-targets to their corresponding estimated latencies.

The WCBLE algorithm is presented in Algorithm~\ref{alg:wcble}.
Its training phase is visualized in~Figure~\ref{fig:diagram-train}.
The initial training epochs $\{\mat{X}_n^{(1)}\}_{n=1}^N$ are set to $\{\mat{X}_n^\mathrm{train}\}_{n=1}^N$.
At every iteration, classifier $\mathcal{C}$ is trained like in CBLE:
\begin{equation}
  \theta^{(i)} =
  \mathrm{train}_\mathcal{C}(\{\mat{X}^{(i-1)}_n[:,s_1:s_2]\}_{n=1}^N,\mathbf{l}^\mathrm{train})
\end{equation}
Next, latency $s_{l_n}^{(i)}$ is determined for every epoch $\mat{X}^{(i)}$ corresponding
to its class label $l_n$ using equation~\ref{eq:prob-latency}.
Finally, the training epochs $\mat{X}^{(i+1)}$ for the next iteration are determined by aligning
each original training epoch to the latency $s_{l_n}^{(i)}$ corresponding to its respective class
label.
\begin{equation}
  \mat{X}^{(i+1)}_n = \mathrm{align}(\mat{X}_n^\mathrm{train}, s_{l_n}^{(i)}) \quad \forall \quad n=1,\ldots,N
\end{equation}
Aligning is performed by shifting and zero-padding the signal to the right if
the latency is negative relative to the time window onset, and to the left if
positive, by the difference between the latency and the window onset.
%\begin{figure}
%	\includegraphics[width=\linewidth]{figures/wcble/figure1.pdf}
%	\caption{Schematic representation of the Woody Classifier Based Latency
%    Estimation training phase.
%    (1) The first-stage spatiotemporal binary classifier is trained on a set of
%    epochs.
%    (2) It is	then applied to time-shifted copies of the epochs to obtain scores
%    and class probabilities	over time.
%    (3) The medians of these probability distributions are assumed the class
%    latencies.
%    (4) The epochs are aligned to their corresponding	class latencies by
%    shifting in time such that all latencies fall at the same moment.
%    (5) The spatiotemporal classifier is then retrained on the aligned epochs
%    for a	next iteration.
%    (6) After the iterative process halts, the scores and	latencies obtained
%    from the last iteration are used to train the second-stage
%		classifier.}
%	\label{fig:diagram-train}
%\end{figure}
\fullpagefig{figures/wcble/figure1.pdf}{Schematic representation of the Woody Classifier Based Latency
    Estimation training phase.
    (1) The first-stage spatiotemporal binary classifier is trained on a set of
    epochs.
    (2) It is	then applied to time-shifted copies of the epochs to obtain scores
    and class probabilities	over time.
    (3) The medians of these probability distributions are assumed the class
    latencies.
    (4) The epochs are aligned to their corresponding	class latencies by
    shifting in time such that all latencies fall at the same moment.
    (5) The spatiotemporal classifier is then retrained on the aligned epochs
    for a	next iteration.
    (6) After the iterative process halts, the scores and	latencies obtained
    from the last iteration are used to train the second-stage
    classifier.}{fig:diagram-train}
The process halts after a fixed amount of iterations or when the estimated set
of latencies has been encountered before, indicating it ended up in a loop.
In the end, the procedure should result in enhanced classifier parameters $\theta^*$,
closer to those when there would be no jitter between epochs.
Note that using the median approach for robust latency estimation results in a
smoother yet longer convergence process compared to the maximum/minimum approach.
We can then apply the classifier with enhanced parameters $\theta^*$ in a CBLE
manner to unseen epochs as illustrated in Figure~\ref{fig:diagram-eval} to obtain a
vector of scores over time as in~Section~\ref{sec:cble} and the estimated latencies as
in~Section~\ref{sec:robust-latency}.
\fullpagefig{figures/wcble/figure2.pdf}{Schematic representation of the Woody Classifier Based Latency
    Estimation test phase. (1) The
		first-stage	spatiotemporal binary classifier obtained from the training phase is
		applied to time-shifted copies of the epochs to obtain scores and class probabilities
		over time. (2) The medians of these probability distributions are assumed
		as the new class latencies. (3) The scores and class latencies are input to the
    trained second-stage classifier, which predicts the label of the epochs.}{fig:diagram-eval}
\section{Algorithms}
\todo{Pr not italic}
\todo{re-insert comments}
\begin{algorithm}[H]
	\textsc{Train}
	\smallskip \hrule \smallskip
	\textbf{Input:} $\{\mat{X}_n^\mathrm{train}\}_{n=1}^N,
  \mathbf{l}^\mathrm{train}, \mathcal{C}(\cdot,f, \Pr), s_1, s_2$
  \begin{algorithmic}[1]
		\State $\theta \gets
			\mathrm{train}_\mathcal{C}(\{\mat{X}_n^\mathrm{train}[:,s_1:s_2]\}_{n=1}^N,\mathbf{l})$
      %\algorithmiccomment{Train stage 1}
		\For{$n=1\ldots N$}
      %\algorithmiccomment{Feature extraction for stage 2}
		  \For{$s=1\ldots R$}
      \State $y_{n,s}^\mathrm{train} \gets f(\mat{X}_n^\mathrm{train}[:,s:s+(s_2-s_1)],\theta)$
        \EndFor
        \State $s_{n,\mathrm{target}}^\mathrm{train} \gets
			    \mathrm{median}\left[Pr(s|\mat{X}_n^\mathrm{train},\theta,\mathrm{target})\right]$
		    \State $s_{n,\mathrm{non-target}}^\mathrm{train}\gets
			    \mathrm{median}\left[Pr(s|\mat{X}_n^\mathrm{train},\theta,\textrm{non-target})\right]$
    \EndFor
	\end{algorithmic}
  \textbf{Output:} $\theta,
  \mat{Y}^\mathrm{train},
  \mathbf{s}_\mathrm{target}^\mathrm{train},
  \mathbf{s}_\mathrm{non-target}^\mathrm{train}$
	\smallskip \hrule \smallskip
	\textsc{Evaluate}
	\smallskip \hrule \smallskip
	\textbf{Input:} $\{\mat{X}_m^\mathrm{test}\}_{m=1}^N, \mathcal{C}(\theta,f, \Pr), s_1, s_2$
  \begin{algorithmic}[1]
		\For{$m=1\ldots M$}
      %\algorithmiccomment{Feature extraction for stage 2}
		  \For{$s=1\ldots R$}
      \State $y_{m,s}^\mathrm{test} \gets f(\mat{X}_n^\mathrm{test}[:,s:s+(s_2-s_1)],\theta)$
        \EndFor
        \State $s_{m,\mathrm{target}}^\mathrm{test} \gets
			    \mathrm{median}\left[Pr(s|\mat{X}_m^\mathrm{test},\theta,\mathrm{target})\right]$
		    \State $s_{m,\mathrm{non-target}}^\mathrm{test}\gets
			    \mathrm{median}\left[Pr(s|\mat{X}_m^\mathrm{test},\theta,\textrm{non-target})\right]$
    \EndFor
	\end{algorithmic}
  \textbf{Output:} $\mat{Y}^\mathrm{test},
  \mathbf{s}_\mathrm{target}^\mathrm{test},
  \mathbf{s}_\mathrm{non-target}^\mathrm{test}$

@@

\newpage
\begin{algorithm}[H]
	\textsc{Train}
	\smallskip \hrule \smallskip
	\textbf{Input:} $\{\mat{X}_n^\mathrm{train}\}_{n=1}^N, \mathbf{l},
		\mathcal{C}(\cdot,f,\Pr), s_1, s_2$
	\begin{algorithmic}[1]
		\State $\mat{X}'_n \gets \mat{X}^\mathrm{train}_n \quad \forall \quad n=1\ldots
    N$
      %\algorithmiccomment{Train stage 1}
		\Repeat
		\State $\theta^* \gets \mathrm{train}_\mathcal{C}(\{\mat{X}'_n[:,s_1:s_2]\}_0^{N-1},\mathbf{l}$
		\For{$n=1\ldots N$}
    \State  $s_n \gets
			    \mathrm{median}\left[Pr(s|\mat{X}_n',\theta^*,l_n)\right]$
		\State $\mat{X}'_n \gets \mathrm{align}(\mat{X}^\mathrm{train}_n, s^*_n)$
		\EndFor
    \Until{convergence or maximum iterations reached}
    \For{$n=1\ldots N$}%\algorithmiccomment{Feature extraction for stage 2}
		  \For{$s=1\ldots R$}
      \State $y_{n,s}^\mathrm{train} \gets
      f(\mat{X}_n^\mathrm{train}[:,s:s+(s_2-s_1)],\theta^*)$
        \EndFor
        \State $s_{n,\mathrm{target}}^\mathrm{train} \gets
			    \mathrm{median}\left[Pr(s|\mat{X}_n^\mathrm{train},\theta^*,\mathrm{target})\right]$
		    \State $s_{n,\mathrm{non-target}}^\mathrm{train}\gets
			    \mathrm{median}\left[Pr(s|\mat{X}_n^\mathrm{train},\theta^*,\textrm{non-target})\right]$
    \EndFor

@@

>>>>

\todo{mention published}
\section{Introduction}

Single-trial ERP latency jitter introduces a problem in ERP analysis:
the \textit{smearing effect} occurs when aggregating over multiple identical
signals with different latencies.
A familiar example of this happens when averaging over jittered epochs for ERP
analysis.
In the presence of jitter, the shape and amplitude of the average do not
reflect the properties of the original signal.
As the smearing effect reduces the amplitude of the average,
it negatively impacts the signal-to-noise ratio (SNR).
The smearing effect equally impacts the SNR of information captured by a
classifier's parameters when training with a procedure that does not account for
this jitter, and thus also affects its performance~\cite{Thompson2012}.
Hence, effective latency estimation and jitter compensation can contribute to higher
decoding performance.
%In this work, we propose a latency estimation and alignment strategy based on
%the method proposed by \cite{Thompson2012}.

@@

\section{Literature}

\subsection{Single-component approaches}
The most straight-forward method to estimate single-trial latency
peak-picking. Here, the latency of an ERP is determined as the
time-point of it's maximum (or minimum) amplitude with relaion to the stimulus
onset. While straight-forward, this method
does not perform well in low or negative SNR conditions, unless combined with
filtering. Filtering can suppress the noise contaminating EEG trials, lowering
the risk of picking a noise peak instead of a true peak of the ERP. Several filtering approaches have been developed to be used in
conjuction with peak-picking, in the time domain~\cite{Carlton1980, McCarthy1981,
	Karjalainen1999, Nishida1999,  Sparacino2002, Georgiadis2005,
	D’Avanzo2011} and in the time-frequency
domain~\cite{Quiroga2003, wang2007single,Hu2010,arico2014influence}. Filtering can
also be done in the spatial domain. The spatial filter can be constructed
using PCA~\cite{Ouyang2017}, ICA~\cite{townsend1999analyzing, jung2001analysis,
	Milne2011}, or as a spatial LCMV beamformer~\cite{TREDER2016279}.

@@

\subsection{Multi-component approaches}
The abovementioned methods do not take into account the fact that  ERPs are multi-component signals. Multiple components can be time-locked to different events or neurophysiological proccess and hence are not necessarily
time-locked to each other. They each can have different latency
variabilities. The presence of more than one component can hamper the
performance of some algorithms, and it often only possible to extract only the
latencies of the largest component present~\cite{Ouyang2017}. When aligning trials
to one component and averaging, this will introduce blurring in the other
components~\cite{Ouyang2020}.

@@

\todo{check overlap with:

@@

}

\subsection{Contribution}

@@

\todo{remove lcmv}
In this work, we introduce a new latency method that leverages data-driven,
joint spatiotemporal filtering based on the LCMV beamformer~\cite{Vliet2016}. The algorithm
integrates the spatiotemporal filtering in Woody's template matching iteration
scheme and can easily be extended to multi-component settings.
Our method attempts to model the spatial and temporal activation of
each ERP component, as well as it's latency distribution, and takes into acount the
spatial and temporal correlation of the EEG background noise.

\section{Methods}

\subsection{Classifier-based Latency Estimation}
\label{sec:cble}

@@

\subsection{Robust CBLE latency features}
\label{sec:robust-latency}
The ERP decoding method based on CBLE introduced by \cite{Mowla2017} does
not make use of the extracted latencies, only passing score matrix $\mat{Y}$ on
to the second-stage classifier.
%Furthermore, previous CBLE works~\cite{Thompson2012,Mowla2020} only used these
%latencies to correlate them with neurophysiological processes or to predict
%decoder performance.
We noticed that, while CBLE performance was unaffected, the classification
performance of our proposed method can be improved if the estimated
latencies are also made available as features to the second-stage classifier,
after a square transform for linear separability~\cite{Thompson2012}.

@@

\subsection{Classifier-based Latency Estimation with Woody
	Iterations}
To improve performance over CBLE, we propose a new algorithm inspired both by
CBLE and the aforementioned Woody iteration scheme (WCBLE).
Instead of using CBLE to estimate the features of a second-stage classifier
directly, CBLE latency estimation is used as a step in a Woody iteration scheme.
While the Woody algorithm iteratively enhances the SNR of an ERP template to
cross-correlate with the data, WCBLE iteratively re-estimates the parameters of
the first-stage classifier.
To improve convergence and perform well in a classification setting, WCBLE
aligns both targets and non-targets to their corresponding estimated latencies.

The WCBLE algorithm is presented in Algorithm~\ref{alg:wcble}.
Its training phase is visualized in~Figure~\ref{fig:diagram-train}.
The initial training epochs $\{\mat{X}_n^{(1)}\}_{n=1}^N$ are set to $\{\mat{X}_n^\mathrm{train}\}_{n=1}^N$.
At every iteration, classifier $\mathcal{C}$ is trained like in CBLE:
\begin{equation}
  \theta^{(i)} =
  \mathrm{train}_\mathcal{C}(\{\mat{X}^{(i-1)}_n[:,s_1:s_2]\}_{n=1}^N,\mathbf{l}^\mathrm{train})
\end{equation}
Next, latency $s_{l_n}^{(i)}$ is determined for every epoch $\mat{X}^{(i)}$ corresponding
to its class label $l_n$ using equation~\ref{eq:prob-latency}.
Finally, the training epochs $\mat{X}^{(i+1)}$ for the next iteration are determined by aligning
each original training epoch to the latency $s_{l_n}^{(i)}$ corresponding to its respective class
label.
\begin{equation}
  \mat{X}^{(i+1)}_n = \mathrm{align}(\mat{X}_n^\mathrm{train}, s_{l_n}^{(i)}) \quad \forall \quad n=1,\ldots,N
\end{equation}
Aligning is performed by shifting and zero-padding the signal to the right if
the latency is negative relative to the time window onset, and to the left if
positive, by the difference between the latency and the window onset.
\fullpagefig{figures/wcble/figure1.pdf}{Schematic representation of the Woody Classifier Based Latency
    Estimation training phase.
    (1) The first-stage spatiotemporal binary classifier is trained on a set of
    epochs.
    (2) It is	then applied to time-shifted copies of the epochs to obtain scores
    and class probabilities	over time.
    (3) The medians of these probability distributions are assumed the class
    latencies.
    (4) The epochs are aligned to their corresponding	class latencies by
    shifting in time such that all latencies fall at the same moment.
    (5) The spatiotemporal classifier is then retrained on the aligned epochs
    for a	next iteration.
    (6) After the iterative process halts, the scores and	latencies obtained
    from the last iteration are used to train the second-stage
    classifier.}{fig:diagram-train}
The process halts after a fixed amount of iterations or when the estimated set
of latencies has been encountered before, indicating it ended up in a loop.
In the end, the procedure should result in enhanced classifier parameters $\theta^*$,
closer to those when there would be no jitter between epochs.
Note that using the median approach for robust latency estimation results in a
smoother yet longer convergence process compared to the maximum/minimum approach.
We can then apply the classifier with enhanced parameters $\theta^*$ in a CBLE
manner to unseen epochs as illustrated in Figure~\ref{fig:diagram-eval} to obtain a
vector of scores over time as in~Section~\ref{sec:cble} and the estimated latencies as
in~Section~\ref{sec:robust-latency}.
\fullpagefig{figures/wcble/figure2.pdf}{Schematic representation of the Woody Classifier Based Latency
    Estimation test phase. (1) The
		first-stage	spatiotemporal binary classifier obtained from the training phase is
		applied to time-shifted copies of the epochs to obtain scores and class probabilities
		over time. (2) The medians of these probability distributions are assumed
		as the new class latencies. (3) The scores and class latencies are input to the
    trained second-stage classifier, which predicts the label of the epochs.}{fig:diagram-eval}
\section{Algorithms}
\todo{Pr not italic}
\todo{re-insert comments}

\begin{algorithm}[H]
	\textsc{Train}
	\smallskip \hrule \smallskip
	\textbf{Input:} $\{\mat{X}_n^\mathrm{train}\}_{n=1}^N,
  \mathbf{l}^\mathrm{train}, \mathcal{C}(\cdot,f, \Pr), s_1, s_2$
  \begin{algorithmic}[1]
		\State $\theta \gets
			\mathrm{train}_\mathcal{C}(\{\mat{X}_n^\mathrm{train}[:,s_1:s_2]\}_{n=1}^N,\mathbf{l})$
      %\algorithmiccomment{Train stage 1}
		\For{$n=1\ldots N$}
      %\algorithmiccomment{Feature extraction for stage 2}
		  \For{$s=1\ldots R$}
      \State $y_{n,s}^\mathrm{train} \gets f(\mat{X}_n^\mathrm{train}[:,s:s+(s_2-s_1)],\theta)$
        \EndFor
        \State $s_{n,\mathrm{target}}^\mathrm{train} \gets
			    \mathrm{median}\left[Pr(s|\mat{X}_n^\mathrm{train},\theta,\mathrm{target})\right]$
		    \State $s_{n,\mathrm{non-target}}^\mathrm{train}\gets
			    \mathrm{median}\left[Pr(s|\mat{X}_n^\mathrm{train},\theta,\textrm{non-target})\right]$
    \EndFor
	\end{algorithmic}
  \textbf{Output:} $\theta,
  \mat{Y}^\mathrm{train},
  \mathbf{s}_\mathrm{target}^\mathrm{train},
  \mathbf{s}_\mathrm{non-target}^\mathrm{train}$
	\smallskip \hrule \smallskip
	\textsc{Evaluate}
	\smallskip \hrule \smallskip
	\textbf{Input:} $\{\mat{X}_m^\mathrm{test}\}_{m=1}^N, \mathcal{C}(\theta,f, \Pr), s_1, s_2$
  \begin{algorithmic}[1]
		\For{$m=1\ldots M$}
      %\algorithmiccomment{Feature extraction for stage 2}
		  \For{$s=1\ldots R$}
      \State $y_{m,s}^\mathrm{test} \gets f(\mat{X}_n^\mathrm{test}[:,s:s+(s_2-s_1)],\theta)$
        \EndFor
        \State $s_{m,\mathrm{target}}^\mathrm{test} \gets
			    \mathrm{median}\left[Pr(s|\mat{X}_m^\mathrm{test},\theta,\mathrm{target})\right]$
		    \State $s_{m,\mathrm{non-target}}^\mathrm{test}\gets
			    \mathrm{median}\left[Pr(s|\mat{X}_m^\mathrm{test},\theta,\textrm{non-target})\right]$
    \EndFor
	\end{algorithmic}
  \textbf{Output:} $\mat{Y}^\mathrm{test},
  \mathbf{s}_\mathrm{target}^\mathrm{test},
  \mathbf{s}_\mathrm{non-target}^\mathrm{test}$

@@

\begin{algorithm}[H]
	\textsc{Train}
	\smallskip \hrule \smallskip
	\textbf{Input:} $\{\mat{X}_n^\mathrm{train}\}_{n=1}^N, \mathbf{l},
		\mathcal{C}(\cdot,f,\Pr), s_1, s_2$
	\begin{algorithmic}[1]
		\State $\mat{X}'_n \gets \mat{X}^\mathrm{train}_n \quad \forall \quad n=1\ldots
    N$
      %\algorithmiccomment{Train stage 1}
		\Repeat
		\State $\theta^* \gets \mathrm{train}_\mathcal{C}(\{\mat{X}'_n[:,s_1:s_2]\}_0^{N-1},\mathbf{l}$
		\For{$n=1\ldots N$}
    \State  $s_n \gets
			    \mathrm{median}\left[Pr(s|\mat{X}_n',\theta^*,l_n)\right]$
		\State $\mat{X}'_n \gets \mathrm{align}(\mat{X}^\mathrm{train}_n, s^*_n)$
		\EndFor
    \Until{convergence or maximum iterations reached}
    \For{$n=1\ldots N$}%\algorithmiccomment{Feature extraction for stage 2}
		  \For{$s=1\ldots R$}
      \State $y_{n,s}^\mathrm{train} \gets
      f(\mat{X}_n^\mathrm{train}[:,s:s+(s_2-s_1)],\theta^*)$
        \EndFor
        \State $s_{n,\mathrm{target}}^\mathrm{train} \gets
			    \mathrm{median}\left[Pr(s|\mat{X}_n^\mathrm{train},\theta^*,\mathrm{target})\right]$
		    \State $s_{n,\mathrm{non-target}}^\mathrm{train}\gets
			    \mathrm{median}\left[Pr(s|\mat{X}_n^\mathrm{train},\theta^*,\textrm{non-target})\right]$
    \EndFor

@@

\section{Results}

\section{Discussion}

\section{Conclusion}
